A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex
Minor corrections.

We begin with an attempt to seprate the notion of item similarity from that of
item popularity. The idea that more popular items are more likely to be
recommended than less popular items motivates an alternative mode for conducting
our random walks over a recommendation graph in order to better isolate item
similarity. We do this by adjusting the probability of transitioning to an item
on the graph by making it inversely proportional to that item's popularity,
$\rho$. Stationary distributions learned from these alternative random walks
better reflect item-item similarity. We find that removing item popularity from
our simulated user data results in better success when mapping between the
derived concept spaces (as evidenced by the improved precision and recall
discussed in the next section).

Next, we reincorporate popularity by modifying how we search for nearest
neighbors in concept space. Instead of simply ranking neighbors by distance, we
now rank by distance divided by $\rho$, thus promoting popular items.  In this
context, having defined popularity as the logorithm of node degree, instead of
simply node degree, reduces the liklihood that one or two very popular items
will always appear as the best recommendations when using this weighted ranking
policy.

@@

In this work, we introduced a novel technique for predicting item-item
associations across retailers. This technique employs {\em Topic-Sensitive
PageRank} on a publicly available recommendation graph to generate simulated
user data. With this data, we perform {\em Latent Semantec Indexing} to learn a
latent feature space for items from in a particular online catalogue. By
generalizing the notion of {\em Term Frequency---Inverse Document Frequency}
score, we construct proxy tf-idf vectors for the latent dimensions, or {\em
concepts}, associated with a particular catalogue. This, in turn, allows us to
construct a transformation matrix such that vectors in one catalogue's concept
space can be transformed into another catalogue's concept space. Inter-catalogue
associations can then be made by finding pairs of items that are a minimal
distance apart in a common concept space.

>>>>

We begin with an attempt to separate the notion of item similarity from that of
item popularity. The idea that more popular items are more likely to be
recommended than less popular items motivates an alternative mode for conducting
our random walks over a recommendation graph in order to better isolate item
similarity. We do this by adjusting the probability of transitioning to an item
on the graph by making it inversely proportional to that item's popularity,
$\rho$. Stationary distributions learned from these alternative random walks
better reflect item-item similarity. We find that removing item popularity from
our simulated user data results in better success when mapping between the
derived concept spaces (as evidenced by the improved precision and recall
discussed in the next section).

Next, we reincorporate popularity by modifying how we search for nearest
neighbors in concept space. Instead of simply ranking neighbors by distance, we
now rank by distance divided by $\rho$, thus promoting popular items.  In this
context, having defined popularity as the logarithm of node degree, instead of
simply node degree, reduces the liklihood that one or two very popular items
will always appear as the best recommendations when using this weighted ranking
policy.

@@

We introduced a novel technique for predicting item-item associations across
retailers. This technique employs {\em Topic-Sensitive PageRank} on a publicly
available recommendation graph to generate simulated user data. With this data,
we perform {\em Latent Semantec Indexing} to learn a latent feature space for
items in a particular online catalogue. By generalizing the notion of {\em Term
Frequency---Inverse Document Frequency} score, we construct proxy tf-idf vectors
for the latent dimensions, or {\em concepts}, associated with a particular
catalogue. This, in turn, allows us to construct a transformation matrix such
that vectors in one catalogue's concept space can be transformed into another
catalogue's concept space. Inter-catalogue associations can then be made by
finding pairs of items that are a minimal distance apart in a common concept
space.
